\texttt{SuperScreen}: An open-source package for simulating the magnetic response of 2D superconductors

### 2021-08-02 main_cpc.tex
Updates from Overleaf

\begin{code}
\begin{minted}[fontsize=\footnotesize]{python}
# Simulate the response to a uniform applied field of 0.2 mT
applied_field = sc.sources.ConstantField(0.2)
field_units = "mT"

@@

\caption{Sheet current $\vec{J}$ and magnetic field $\mu_0H_z$ distributions for the circular (top) and square (bottom) ring calculated using Code Block~\ref{code:ring_circulating_current}.}
\label{fig:ring_circulating_current}
\end{figure}

>>>>

\begin{code}
\begin{minted}[fontsize=\footnotesize]{python}
# Simulate the response to a uniform applied field of 0.25 mT
applied_field = sc.sources.ConstantField(0.25)
field_units = "mT"

@@

\caption{Sheet current $\vec{J}$ and magnetic field $\mu_0H_z$ distributions for the circular (top) and square (bottom) ring calculated using Code Block~\ref{code:ring_circulating_current}.}
\label{fig:ring_plot_fields_currents}
\end{figure}
